%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV in English
%% Bastián González-Bustamante
%% https://github.com/bgonzalezbustamante/CV-LaTeX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,margin]{res} 
\textwidth=5.2in %% increase textwidth to get smaller right margin
\usepackage[sc]{mathpazo}
\usepackage[T1]{fontenc} %% Use 8-bit encoding that has 256 glyphs
%% \linespread{1.05} %% Line spacing - Palatino needs more space between lines
%% \usepackage{helvetica} %% uses helvetica postscript font (download helvetica.sty)
%% \usepackage{newcent}  %% uses new century schoolbook postscript font 

\hyphenation{multi-adhesi\'on mi-nistros suppor-ted Twitter Mexico Demo-cracy methodo-logical Politi-cal Eco-no-my Socio-lo-gy Consti-tu-tional Mana-gement Demo-cracia Demo-cracies descen-tra-liza-ci\'on Spa-nish multi-asociati-va subse-cre-tarios Scien-ce Aproxi-ma-ciones Parti-ci-pa-tion pro-gra-mming Approach Authori-taria-nism Deli-ve-red mo-dels Ine-quali-ties scien-ces Ameri-can Latino-ameri-ca-na Di-gi-tal Go-vern-ment Mi-nis-ters avail-able Trai-ning Know-led-ge Pro-fessio-na-li-sa-tion avail-able Ame-ri-ca ca-pi-tal ho-nours}
\usepackage{ marvosym}
\usepackage{graphicx}
\usepackage{wrapfig}

\usepackage{fancyhdr} %% Headers and footers
\pagestyle{fancy} %% Every page with header and footers
\fancyhead{} %% Blank out the default header
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[LO,RE]{} %% Blank out the default footer
\fancyfoot[RO,LE]{\small {\thepage} of 5} %% Custom footer text
\fancyfoot[C]{} 

\usepackage[english]{babel}

\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}

\usepackage{fontawesome} %% Icons 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pdfinfo{
   /Author (Basti\'an Gonz\'alez-Bustamante)
   /Title  (Executive Curriculum Vitae)
   /Subject (Curriculum Vitae)
   /Keywords (Curriculum)
}

\newenvironment{benumerate}[1]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}
}{
    \end{enumerate}
}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\setlist[enumerate]{leftmargin=*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document} 
 
\name{{\large Basti\'an Gonz\'alez-Bustamante}\\[15pt]} 
 
\address{{\small Department of Politics and International Relations} \\ {\small \& St Hilda's College} \\ {\small University of Oxford} \\ {\small St Hilda's College, Cowley Place, Oxford OX4 1DY} \\}
\address{{\large \Letter} {\small \href{mailto:bastian.gonzalezbustamante@politics.ox.ac.uk}{bastian.gonzalezbustamante@politics.ox.ac.uk}} \\ {\large \Letter} {\small \href{mailto:bastian.gonzalezbustamante@st-hildas.ox.ac.uk}{bastian.gonzalezbustamante@st-hildas.ox.ac.uk}} \\ {\small \href{http://users.ox.ac.uk/~shil5311/}{http://users.ox.ac.uk/$\sim$shil5311}} \\ {\small } \\ [5pt]} %% 

\begin{resume} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Expertise}

{\small {\itshape Research interests:} Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service systems, electoral participation, digital media, online social networks, electronic and open government}

{\small {\itshape Statistical techniques:} Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social network analysis, qualitative comparative analysis,  topic modelling}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
\section{\footnotesize Education}

{\small {\bfseries DPhil in Politics}, University of Oxford, {\scshape gbr}} \hfill {\small 2019 -- ongoing}\\
{\small Professor Petra Schleiter (Supervisor)}
%% {\footnotesize Proposed thesis: Critical Events and Ministerial Turnover in Latin American Presidential Democracies}

{\small {\bfseries MA in Political Science}, Universidad de Chile, {\scshape chl}} \hfill {\small 2010 -- 2013}\\
{\small Highest Distinction (1st, First-class honours)}
%% {\small \itshape Main courses: Quantitative and Qualitative Methods, Political Sociology, Political Systems and Democracies, International Relations, and Political Thought.} 

{\small {\bfseries BA in Government and Political Sciences}, Universidad de Chile, {\scshape chl}}  \hfill {\small 2004 -- 2009}\\
{\small Distinction (2:1, Second-class honours, upper division)}
%% {\small \itshape Main courses: Political Science, Political Thought, Sociological Theory, International Relations, Public Policies, Theory of Science, Applied Statistics, and Social Research Methods.}\\

{\small {\bfseries Public Service Administrator}, Universidad de Chile, {\scshape chl}}  \hfill {\small 2004 -- 2009}\\
{\small Distinction (2:1, Second-class honours, upper division)}
%% {\small \itshape Main courses: Government and Public Management, Organizational Theory, Administrative Theory, Constitutional Law, Administrative Law, Accounting, Economics, Organizational Design and Process Management, Human Resources Management, and Planning.}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \section{\footnotesize Relevant \\ Employment}
 
%% {\small {\bf Faculty Member}, Instructor Professor} \hfill {\small 2018 -- ongoing}\\
{\bf \small Instructor} \hfill {\small 2018 -- ongoing}\\
{\small Department of Public Administration and Policy} \hfill {\scshape \footnotesize [Leave of Absence]}\\
{\small Faculty of Economics and Management, Universidad de Santiago, {\scshape chl}}

%% {\bf \small Research Associate} \hfill {\small 2020 -- ongoing}\\
%% {\small Media Research Programme}\\
%% {\small Department of Journalism Studies, Universidad Alberto Hurtado, {\scshape chl}}

{\bf \small Consultant} \hfill {\small 2016 -- 2017}\\
{\small Democratic Governance Programme}\\
{\small United Nations Development Programme ({\scshape UNDP}), {\scshape chl}}

{\small \bf Adjunct Professor} \hfill {\small 2014 -- 2017}\\
{\small Department of Public Administration and Policy}\\
{\small Faculty of Economics and Management, Universidad de Santiago, {\scshape chl}}

%% {\small \bf Lecturer} \hfill {\small 2013 -- 2016}\\
%% {\small School of Government and Public Management}\\
%% {\small Institute for Public Affairs, Universidad de Chile, {\scshape chl}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Peer-Reviewed \\ Articles in Social Sciences Citation \\ Index Journals}

\begin{benumerate}{5}
\item{\small Gonz\'alez-Bustamante, B. ({\itshape forthcoming}). Evolution and Early Government Responses to COVID-19 in South America. {\itshape World Development}. {\footnotesize \scshape [{\bfseries \small 3.869} 2019-JIF, {\bfseries \small Q1} Economics]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., Carvajal, A., \& Gonz\'alez, A. (2020). Determinants of E-Government in the Municipalities: Evidence from the Chilean Case. {\itshape Gesti\'on y Pol\'itica P\'ublica, XXIX}(1), 97--129. {\footnotesize \scshape [in Spanish, {\bfseries \small 0.222} 2019-JIF, {\bfseries \small Q4} Public Administration]}. {\scshape doi:} \href{http://dx.doi.org/10.29265/gypp.v29i1.658}{10.29265/gypp.v29i1.658}. \\ {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/fze3x}{10.31235/osf.io/fze3x}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2019). The Politics-Administration Dichotomy: A Case Study of the Chilean Executive During the Democratic Post-Transition. {\itshape Bulletin of Latin American Research}. Early View. {\footnotesize \scshape [{\bfseries \small 0.586} 2019-JIF, {\bfseries \small Q3} Area Studies]}. {\scshape doi}: \href{https://doi.org/10.1111/blar.13044}{10.1111/blar.13044}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2019). Gaps, Representation, and Elite-Mass Congruence in Chile and Uruguay. {\itshape Convergencia. Revista de Ciencias Sociales}, (80), 1-27. {\footnotesize \scshape [in Spanish, {\bfseries \small 0.704} 2019-JIF, {\bfseries \small Q4} Sociology]}. {\scshape doi}: \href{https://doi.org/10.29101/crcs.v26i80.11097}{10.29101/crcs.v26i80.11097}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/cqym8}{10.31235/osf.io/cqym8}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialization, Trajectories and Post-Career of Ministers in Chile, 1990-2010. {\itshape Pol\'itica y Gobierno, XXV}(1), 31-64. {\footnotesize \scshape [in Spanish, {\bfseries \small 0.714} 2019-JIF, {\bfseries \small Q4} Political Science]}. {\scshape url}: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{www.politicaygobierno.cide.edu}}
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% \section{\footnotesize Under Review in \\ Social Sciences Citation Index \\ Journals}

%% \begin{benumerate}{2}
%% \item{\small Garrido-Vergara, L., \& Gonz\'alez-Bustamante, B. (2019). Public Opinion and Stateness: Evidence from the Chilean Case. {\footnotesize \scshape [in Spanish, 1st r\&r]}.}\vspace{1mm}

%% \item{\small Barr\'ia, D., \& Gonz\'alez-Bustamante, B. (2018). Explaining Transparency in Chilean Local Governments. {\footnotesize \scshape [1st r\&r]}.}
%% \end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Peer-Reviewed \\ Edited Volumes}

\begin{benumerate}{2}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. {\itshape Pleyade}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2016). Political, Economic, and Intellectual Elites. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1). {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{https://revistapolitica.uchile.cl}}
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Peer-Reviewed \\ Articles in Scopus \\ \& Emerging \\ Sources Citation \\ Index Journals}

\begin{benumerate}{7}
\item{\small Olivares, A. {\itshape et al.} (2020). New Challenges, Approaches, and Perspectives in the Study of Political Elites. {\itshape Iberoamericana, XX}(74), 229--259. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://journals.iai.spk-berlin.de/index.php/iberoamericana/article/view/2736}{https://journals.iai.spk-berlin.de}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/syqu4}{10.31235/osf.io/syqu4}}\vspace{1mm}

\item{\small Maillet, A. , Gonz\'alez-Bustamante, B., \& Olivares, A. (2019). Public-Private Circulation and the Revolving Door in the Chilean Executive Branch (2000-2014). {\itshape Latin American Business Review, 20}(4), 367--387. {\scshape doi}: \href{https://doi.org/10.1080/10978526.2019.1652099}{10.1080/10978526.2019.1652099}}\vspace{1mm}

\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Cisternas, C. (2019). The Literature on Open Government in Spanish. Analysis of the Dynamics of Production and Citation. {\itshape N\'oesis. Revista de Ciencias Sociales y Humanidades, 28}(56), 22-42. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://dx.doi.org/10.20983/noesis.2019.2.3}{10.20983/noesis.2019.2.3}}\vspace{1mm}

\item{\small Del Valle, N., \& Gonz\'alez-Bustamante, B. (2018). Political Agenda, Journalism and Digital Media in Chile: Research Notes on Media Pluralism. {\itshape Perspectivas de la Comunicaci\'on, 11}(1), 291-326. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://revistas.ufro.cl/ojs/index.php/perspectivas/article/view/1146}{http://revistas.ufro.cl}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2016). Cabinet Turnover and Survival of Ministers in Chile During the Concertacion Governments (1990-2010). {\itshape Colombia Internacional}, (87), 81-108. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{https://doi.org/10.7440/colombiaint87.2016.04}{10.7440/colombiaint87.2016.04}}\vspace{0.9mm}

\item{\small Gonz\'alez-Bustamante, B. {\itshape et al.} (2016). Civil Service in Chile, Analysis of Senior Civil Servants on the Top Rung of the Hierarchy (2003-13). {\itshape Revista de Administra\c{c}\~ao P\'ublica, 50}(1), 59-79. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://dx.doi.org/10.1590/0034-7612145767}{10.1590/0034-7612145767}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2015). Undersecretaries Rotation in Chile: An Exploration of the Second Government Line, 1990-2014. {\itshape Revista de Gesti\'on P\'ublica, IV}(2), 151-190. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/321977889_Rotacion_de_subsecretarios_en_Chile_una_exploracion_de_la_segunda_linea_gubernamental_1990-2014}{https://www.researchgate.net}}
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Peer-Reviewed \\ Articles in SciELO \\ \& Latindex \\ Journals}

\begin{benumerate}{9}
\item{\small Gonz\'alez-Bustamante, B. (2016). Political, Economic, and Intellectual Elites: A Growing Research Agenda for Political Science. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 7-17. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42690}{https://revistapolitica.uchile.cl}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2016). Political Elites in the Chilean Legislative Branch: The Chamber of Deputies (1990-2014). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1), 19-52. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/42691}{https://revistapolitica.uchile.cl}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2015). Assessing Twitter as a Public Opinion Measure: An Exploration of the Bachelet's Arrival to the Chilean Presidential Campaign 2013. {\itshape Revista SAAP, 9}(1), 119-141. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://ref.scielo.org/dwzhns}{http://ref.scielo.org}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2015). Electoral Success and Campaign Spending in Elections of Senators and Deputies in Chile 2013. {\itshape Pol\'iticas P\'ublicas, 8}(1), 21-35. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://www.revistas.usach.cl/ojs/index.php/politicas/article/view/2182}{www.revistas.usach.cl}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2014). Popular Election of Regional Councillors 2013. Performance of Political, Family, and Economic Capital in a New Electoral Arena in Chile. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 52}(2), 49-91. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/36137}{https://revistapolitica.uchile.cl}}\vspace{1mm}

\item{\small Olivares, A. {\itshape et al.} (2014). Think Tanks in the Cabinet: An Exploration of the Chilean Case (2006-2014). {\itshape Revista de Sociolog\'ia,} (29), 37-54. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://revistadesociologia.uchile.cl/index.php/RDS/article/view/36177}{https://revistadesociologia.uchile.cl}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2013). Factors Affecting Access and Permanence of the Governmental Political Elite in Chile (1990-2010). {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 51}(1), 119-153. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/article/view/27436}{https://revistapolitica.uchile.cl}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2013). The Study of the Elites in Chile: Theoretical and Methodological Approaches. {\itshape Intersticios Sociales,} (6), 1-20. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{http://ref.scielo.org/zrnp2k}{http://ref.scielo.org}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G. (2012). Digital Campaigns: Branding or Political Participation? {\itshape M\'as Poder Local,} (12), 32-39. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/260517478_Campanas_digitales_Branding_o_participacion_politica_El_rol_de_las_redes_sociales_en_la_ultima_campana_presidencial_chilena}{https://www.researchgate.net}}
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Peer-Reviewed \\ Book Chapters}

\begin{benumerate}{11}
\item{\small Gonz\'alez-Bustamante, B. (2018). Civil Service Models in Latin America. In A. Farazmand (ed.), {\itshape Global Encyclopedia of Public Administration, Public Policy, and Governance}. Cham: Springer. {\scshape doi}: \href{https://doi.org/10.1007/978-3-319-20928-9\_2699}{10.1007/978-3-319-20928-9\_2699}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/mp4qd}{10.31235/osf.io/mp4qd}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2018). Internet, Digital Social Networks Usage, and Participation in the Southern Cone. In P. Cottet (ed.), {\itshape Opini\'on P\'ublica Contempor\'anea: Otras Posibilidades de Comprensi\'on e Investigaci\'on}. Santiago: Social-Ediciones. {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Olivares, A. (2018). Governmental Political Elite in Chile: Ministers Survival (1990-2014). In A. Codato \& F. Espinoza (eds.), {\itshape Las \'Elites en las Am\'ericas: Diferentes Perspectivas}. Curitiba: Editora UFPR. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://www.researchgate.net/publication/325699783_Elites_en_las_Americas_diferentes_perspectivas_Elites_in_the_Americas_Different_Perspectives}{https://www.researchgate.net}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Barr\'ia, D. (2018). Expansion of the Public Sphere in Chile: Social Networks, Electoral Campaigns, and Digital Participation. In N. Del Valle (ed.), {\itshape Transformaciones de la Esfera P\'ublica en Chile. Luchas Sociales, Espacio P\'ublico y Pluralismo Informativo}. Santiago: RIL. {\footnotesize \scshape [in Spanish]}. {\scshape {\footnotesize SocArXiv} doi}: \href{https://doi.org/10.31235/osf.io/nkftb}{10.31235/osf.io/nkftb}}\vspace{1,1mm}

\item{\small Barr\'ia, D., Gonz\'alez-Bustamante, B., \& Araya, J. E. (2017). Electronic Democracy and Digital Participation: Advances and Challenges. In J. R. Gil-Garc\'ia, J. I. Criado \&  J. C. T\'ellez (eds.), {\itshape Tecnolog\'ias de Informaci\'on y Comunicaci\'on en la Administraci\'on P\'ublica: Conceptos, Enfoques, Aplicaciones y Resultados}. Mexico City: INFOTEC. {\footnotesize \scshape [in Spanish]}. \\ {\scshape url}: \href{https://www.researchgate.net/publication/321980289_Democracia_electronica_y_participacion_digital_Avances_y_desafios}{https://www.researchgate.net}}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2016). Twitter Usage in Political Communication. In I. Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}. Madrid: CEPC. {\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D. (2016). Viral Campaign. In I. Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}. Madrid: CEPC. {\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Sazo, D. (2016). Political Branding. In I. Crespo {\itshape et al.} (eds.), {\itshape Diccionario Enciclop\'edico de Comunicaci\'on Pol\'itica}. Madrid: CEPC. {\footnotesize \scshape [in Spanish, 2nd edition]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2014). New Media and Digital Politics: The Case of Chilean Primary Presidential Elections 2013. In G. Sibaja (ed.), {\itshape Nuevos medios y comunicaci\'on pol\'itica digital}. San Jose: FESJD. {\footnotesize \scshape [in Spanish]}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2014). Digital Activism, Social Networks, and Brokerage. In S. Millaleo \& P. C\'arcamo (eds.), {\itshape Mediaciones del sistema pol\'itico frente al activismo digital}. Santiago: FDD. {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://www.researchgate.net/publication/321992867_Activismo_digital_redes_sociales_e_intermediacion}{https://www.researchgate.net}}\vspace{1mm}

%% Gonz\'alez--Bustamante, B. (2014). Redes sociales como herramienta para la pr\'actica pol\'itica: Twitter y el concepto de opini\'on p\'ublica. In O. Avil\'es, R. C\'arcamo, J. Illanes, B. Jul, \& T. Laibe (Eds.), {\itshape Pr\'actica pol\'itica y medios digitales}. Santiago, Chile: Instituto Igualdad. %%(pp. 77--98)

\item{\small Gonz\'alez-Bustamante, B., \& Henr\'iquez, G. (2013). Chile: The Digital Campaign 2009-2010. In I. Crespo \& J. del Rey (eds.), {\itshape Comunicaci\'on Pol\'itica \& Campa\~nas Electorales en Am\'erica Latina}. Buenos Aires: Biblos. {\footnotesize \scshape [in Spanish].}}
\end{benumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Selected \\ Conference Presentations}

\begin{itemize}
\item{\small International Political Science Association, {\scshape esp} 2012, {\scshape prt} 2021}
%% \item{\small Chilean Association of Communication Researchers Congress, {\scshape chl} 2020}
\item{\small Latin American Studies Association, {\scshape usa} 2016, 2019}
\item{\small Latin American Association of Electoral Camp. Researchers, {\scshape mex} 2013, {\scshape esp} 2012, 2018}
\item{\small Chilean Political Science Association, {\scshape chl} 2012, 2014, 2016, 2018}
\item{\small Latin American Political Science Association, {\scshape ecu} 2012, {\scshape col} 2013, {\scshape per} 2015, {\scshape ury} 2017}
\item{\small Chilean Sociology Association, {\scshape chl} 2012, 2016}
\item{\small Argentine Association of Political Analysis, {\scshape arg} 2013, 2015}
\item{\small World Association for Public Opinion Research, {\scshape chl} 2014}
\item{\small Latin American Sociology Association, {\scshape chl} 2013}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Relevant \\ Teaching \\ Experience} %% \vspace{1,5mm}

\begin{itemize}
\item{\small Department of Politics and International Relations, University of Oxford, {\scshape gbr}}
\begin{itemize}
\item[$\circ$]{\small {\bf Comparative Government} (undergraduate tutorial, Prof. Petra Schleiter), Hilary 2020}
\end{itemize}
\end{itemize}

\begin{itemize}
\item{\small Faculty of Economics and Management, Universidad de Santiago, {\scshape chl}}
\begin{itemize}
\item[$\circ$]{\small {\bf Political Science I} (undergraduate lecture), Spring 2014, 2018, Fall 2015-2019}
\item[$\circ$]{\small {\bf Political Science II} (undergraduate lecture), Spring 2015-2018}
\item[$\circ$]{\small {\bf Econometrics for Public Policies} (undergraduate lecture), Fall 2018}
\item[$\circ$]{\small {\bf Workshop for Research Design} (graduate seminar), Spring 2017-2018}
\item[$\circ$]{\small {\bf Research Methodology} (undergraduate lecture), Spring 2014-2015, Fall 2015-2017}
\item[$\circ$]{\small {\bf Introduction to Quantitative Methods} (undergraduate lecture), Fall 2017}
\end{itemize}
\item{\small School of Government and Public Management, Universidad de Chile, {\scshape chl}}
\begin{itemize}
\item[$\circ$]{\small {\bf Study of Political Phenomena} (undergraduate lecture), Fall 2016}
\item[$\circ$]{\small {\bf Political Analysis} (undergraduate lecture), Fall 2014}
\item[$\circ$]{\small {\bf Elite Theory and Democracy} (undergraduate lecture, Prof. Alejandro Olivares), Spring 2013-2014}
%% \item[$\circ$]{\small {\bf Study of Government} (undergraduate tutorial, Prof. Karina Do\~na), Fall 2009}
%% \item[$\circ$]{\small {\bf Organisational Theory} (undergraduate tutorial, Prof. Patricio Castro), Spring 2008}
\end{itemize}
%% \item{\small  Faculty of Political Science and Public Administration, Universidad Central, {\scshape chl}}
%% \begin{itemize}
%% \item[$\circ$]{\small {\bf E-Government} (undergraduate lecture), Spring 2015}
%% \end{itemize}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Honours \& \\ Awards} 

\begin{itemize}
\item{\small {\bfseries St Hilda's College at the University of Oxford Book and Travel Grants}. Allowances for books and conference participation (travel grant was declined because of coronavirus pandemic), Oxford, {\scshape gbr} 2020, {\pounds} 745}
\item{\small {\bfseries Becas Chile Doctoral Scholarship Abroad}. Tuition fees, transport and living expenses for pursuing a DPhil at the University of Oxford ({\scshape anid/pfcha}/72200340), Oxford, {\scshape gbr} 2019-2023, {\pounds} 160,000}
\item{\small {\bfseries LASA Travel Grant}. Travel support for the XXXIV International Congress of the Latin American Studies Association ({\scshape lasa}/40071), New York, {\scshape usa} 2016, {\pounds} 400}
\item{\small {\bfseries CESS Summer School Scholarship}. Financial support for the Experimental Summer School Methods at the Nuffield-USACH Centre for Experimental Social Sciences ({\scshape cess}), Santiago, {\scshape chl} 2016, {\pounds} 200}
\item {\small {\bfseries ALACIP Methodological School Prize}. Best methodological work at the Latin American Political Association School ({\scshape alacip}), Lima, {\scshape per} 2015}
\item{\small {\bfseries ACCP Winter School Scholarship}. Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association ({\scshape accp}), Montevideo, {\scshape ury} 2015, {\pounds} 300}
\item{\small {\bfseries PUC Summer School Scholarship}. Financial support for the Summer School in Mixed Methods at the Pontificia Universidad Cat\'olica de Chile ({\scshape puc}), Santiago, {\scshape chl} 2014, {\pounds} 170}
\item{\small {\bfseries Comunicracia Prize}. Best paper of the XI Argentinian Congress of Political Science political communication area (double-blind peer-review), Parana, {\scshape arg} 2013, {\pounds} 170}
\item{\small {\bfseries Highest Rating MA Dissertation}. The highest rating and the congratulations from the jury at the Universidad de Chile, Santiago, {\scshape chl} 2013}
\item{\small {\bfseries FONDECYT Thesis Writing Grant}. Financial support for MA field work (Prof. Gonzalo Delamaza, Supervisor, {\scshape anid/fondecyt}/1100877), Santiago, {\scshape chl} 2012-2013, {\pounds} 1,150} %% (Supervisor: G. Delamaza, Co-Supervisor: A. Joignant, Examiners: J. Baeza and M. D\'avila) %% (A. Joignant, Principal Researcher)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Service as a Peer Reviewer \& Expert}

\begin{itemize}
\item{\small Varieties of Democracy Project, University of Gothenburg, {\scshape swe} 2014, 2018-2020}
\item{\small Global Academic Reputation Survey, Clarivate Analytics, {\scshape usa} 2020}
\item{\small Sectoral Commission for Research, Universidad de la Rep\'ublica, {\scshape ury} 2016, 2018}
\item{\small Times Higher Education World University Rankings, {\scshape elsevier} 2018-2019}
\item{\small Reviewer in {\scshape WoS} \& {\scshape Scopus} journals, 2013-2020}
\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, 2013-2020}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Current \\ Memberships}

{\small International Political Science Association, Latin American Studies Association, Latin American Council for Social Sciences, Latin American Political Science Association, Latin American Association of Electoral Campaign Researchers, and Chilean Political Science Association}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Languages}

{\small Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), and French (elemental reading skills)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Softwares \& Programming}

{\small R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}, Notepad{\footnotesize ++}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\footnotesize Full CV \\ Upon Request}

{\small The full version includes the following additional information: a brief biography, other employment and publications, full list of conference and seminar presentations, whole teaching experience, full list of journals where I have been a reviewer, academic and conference service, skills certification and training, and references available to contact. Please request it by email {\large \Letter} \href{mailto:bastian.gonzalezbustamante@politics.ox.ac.uk}{bastian.gonzalezbustamante@politics.ox.ac.uk}}\\

\section{}
{\footnotesize Executive CV {\scshape pdf} version (five pages, 137 {\scshape kb}) typed in {\small {\LaTeX}} with hyperlinks}\\
{\footnotesize Last updated: July 29, 2020}\\
{\footnotesize {\normalsize \faGithub} \href{https://bgonzalezbustamante.github.io/CV-LaTeX/}{Download the latest version}.}

\end{resume} 
\end{document} 
